---
title: "Bevel Probabilistic Selection Task Performance"
output:
  html_document:
    df_print: paged
  html_notebook: default
  word_document: default
---
## Task Information
Total Number of Trials = 104 
Sweet taste and bitter taste was selected by participant to reflect reward & punishment

## Learning Curve by Shape Pair

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(reshape)

data <- read.delim("~/Documents/bevel_choice/all_subjects.txt")
names(data) <- c("subj", "run", "pair", "choice", "outcome", "congruent", "RT")

data <- data %>%
  group_by(.dots=c("subj","pair")) %>%
  mutate(Count=row_number())

percent_correct_by_trial_ab <- function(n) {
  count <- sum(data$Count == n & data$choice=="corr" & data$pair == "12")
  countall <- sum(data$Count == n & data$pair == "12")
  return(count/countall)
}

percent_correct_by_trial_cd <- function(n) {
  count <- sum(data$Count == n & data$choice=="corr" & data$pair == "34")
  countall <- sum(data$Count == n & data$pair == "34")
  return(count/countall)
}

percent_correct_by_trial_ef <- function(n) {
  count <- sum(data$Count == n & data$choice=="corr" & data$pair == "56")
  countall <- sum(data$Count == n & data$pair == "56")
  return(count/countall)
}

#percent_correct_by_trial_ab(10)

x <- 1:46
output_ab <- lapply(x, percent_correct_by_trial_ab) 
output_cd <- lapply(x, percent_correct_by_trial_cd) 
output_ef <- lapply(x, percent_correct_by_trial_ef) 

df_ab <- data.frame(matrix(unlist(output_ab), nrow=length(output_ab), byrow=T))
df_cd <- data.frame(matrix(unlist(output_cd), nrow=length(output_cd), byrow=T))
df_ef <- data.frame(matrix(unlist(output_ef), nrow=length(output_ef), byrow=T))

colnames(df_ab)[colnames(df_ab)=="matrix.unlist.output_ab...nrow...length.output_ab...byrow...T."] <- "percent_correct_ab"
colnames(df_cd)[colnames(df_cd)=="matrix.unlist.output_cd...nrow...length.output_cd...byrow...T."] <- "percent_correct_cd"
colnames(df_ef)[colnames(df_ef)=="matrix.unlist.output_ef...nrow...length.output_ef...byrow...T."] <- "percent_correct_ef"

df_ab$trialnum<-row.names(df_ab)
df_cd$trialnum<-row.names(df_cd)
df_ef$trialnum<-row.names(df_ef)
#head(df_ab$trialnum)

data0<-merge(df_ab, df_cd, by="trialnum")
data1<- merge(data0, df_ef, by="trialnum")

df_ab$trial <- seq.int(nrow(df_ab))
df_cd$trial <- seq.int(nrow(df_cd))
df_ef$trial <- seq.int(nrow(df_ef))

```

#Learning Curves for each Shape Pair
```{r}
plot1 <- ggplot(data=df_ab, aes(x=trial, y=percent_correct_ab, group=1)) +
  geom_line()+
  geom_point() +
  theme_classic() + scale_x_continuous(name="Trial Number") +
  scale_y_continuous(name="Percent of Sample choosing 80% Shape")

plot2 <- ggplot(data=df_cd, aes(x=trial, y=percent_correct_cd, group=1)) +
  geom_line()+
  geom_point() + 
  theme_classic() + scale_x_continuous(name="Trial Number") +
  scale_y_continuous(name="Percent of Sample choosing 70% Shape") 

plot3 <- ggplot(data=df_ef, aes(x=trial, y=percent_correct_ef, group=1)) +
  geom_line()+
  geom_point() + 
  theme_classic() + scale_x_continuous(name="Trial Number") +
  scale_y_continuous(name="Percent of Sample choosing 60% Shape")

plot1
plot2
plot3
```


# Learning Curves Overlaid 
```{r}
ggplot(data1, aes(as.numeric(trialnum))) + 
  geom_line(aes(y = percent_correct_ab, colour = "80/20 pair")) + 
  geom_line(aes(y = percent_correct_cd, colour = "70/30 pair")) + 
  geom_line(aes(y = percent_correct_ef, colour = "60/40 pair")) +
  theme_classic() + scale_x_continuous(name="Trial Number") +
  scale_y_continuous(name="Percent of Sample choosing Higher %Correct Shape") +
  labs(colour = "Shape Pair")
  
```



```{r}
library(ggplot2)
library(ggpubr)
library(plyr)
library(tidyverse)
library(reshape)
library(data.table)
```


## Possible outcomes
80-20  == 12
70-30  == 34
60-40  == 56

```{r}
sub1<-read.table("~/Documents/bevel_choice/by_participant_txtfiles/50.txt", sep="\t", header=F)
head(sub1)
names(sub1)<-c("sub_num","run","type","choice","side","outcome","congruent","RT")
head(sub1)
sub1$side<-as.factor(sub1$side)
sub1$side<-revalue(sub1$side, c("1"="left", "2"="right"))
sub1$trial<-row.names(sub1)
head(sub1)
```

```{r}
cbPalette <- c("00900","FF3300")

plot1<-ggplot(subset(sub1, type == "EF"), aes(trial,side, group=as.factor(side)))+
  geom_line()+
  geom_point(aes(color=as.factor(congruent), shape=as.factor(outcome)), size=5)+
  scale_fill_manual(cbPalette)+
  theme_classic()


plot2<-ggplot(subset(sub1, type == "CD"), aes(trial,side, group=as.factor(side)))+
  geom_line()+
  geom_point(aes(color=as.factor(congruent), shape=as.factor(outcome)),  size=5)+
  scale_fill_manual(cbPalette)+
  theme_classic()

plot3<-ggplot(subset(sub1, type == "AB"), aes(trial,side, group=as.factor(side)))+
  geom_line()+
  geom_point(aes(color=as.factor(congruent), shape=as.factor(outcome)),  size=5)+
  geom_point(aes(shape=as.factor(choice)))+
  theme_classic()+
  scale_fill_manual(cbPalette)

ggarrange(plot1,plot2,plot3, 
          labels = c("60-40", "70-30","80-20"),
          ncol = 1, nrow = 3)
```


```{r}
plot3<-ggplot(subset(sub1, type == "AB"), aes(as.numeric(trial),side, group=as.factor(side)))+
  geom_line()+
  geom_point(aes(color=as.factor(congruent), shape=as.factor(outcome)),  size=10)+
  geom_point(aes(shape=as.factor(choice), color=as.factor(congruent)), size=5)+
  theme_classic()+
  scale_fill_manual(cbPalette)
plot3
```
Left right, not informative. 

```{r}
x<-subset(sub1, type == "AB")
summary(as.factor(x$choice))
summary(x)
```
data$ov_ob[BMI<18.5]<-"Underweight"
```{r}
sub1$outcome0[sub1$outcome == "Miss"] <- 0
sub1$outcome0[sub1$outcome == "punish"] <- -10
sub1$outcome0[sub1$outcome == "reward"] <- 10

hm1<-ggplot(sub1,aes(as.numeric(trial), sub_num ,fill=outcome0))+
  geom_tile()+
  scale_fill_gradient2(low="blue", high="red", na.value="black", name="")+
  geom_point(aes(shape=as.factor(choice), size=10, color=as.factor(choice)))
hm1
  

```


# Super clever function to read in a shit ton of data

```{r}
readdata <- function(fn){
    dt_temp <- fread(fn, sep="\t")
    return(dt_temp)
}

all.files <- list.files(path = "~/Documents/bevel_choice/by_participant_txtfiles/",pattern = ".txt", full.names = TRUE)
mylist <- lapply(all.files, readdata)
mydata <- rbindlist(mylist, use.names=FALSE)

names(mydata)<-c("sub_num","run","type","choice","side","outcome","congruent","RT")
mydata$side<-as.factor(mydata$side)
mydata$side<-revalue(mydata$side, c("1"="left", "2"="right"))

mydata <- mydata %>%
 group_by(.dots=c("sub_num")) %>%
 dplyr::mutate(Count=row_number())

head(mydata)
mydata$sub_num
```


```{r}
mydata$outcome0[mydata$outcome == "Miss"] <- 0
mydata$outcome0[mydata$outcome == "punish"] <- -10
mydata$outcome0[mydata$outcome == "reward"] <- 10

hmTOTAL<-ggplot(mydata,aes(as.numeric(Count), as.factor(sub_num) ,fill=outcome0))+
  geom_tile()+
  scale_fill_gradient2(low="blue", high="red", na.value="black", name="")+theme_classic()+
  geom_point(aes(shape=as.factor(choice), size=1, color=as.factor(choice)))
hmTOTAL
  

```

```{r}
more_data<-read.table("~/Documents/bevel_choice/clean_bevel.csv",header=T, sep=",")
more_data$sub_num<-row.names(more_data)
head(more_data$sub_num)

data0<-merge(mydata, more_data, by="sub_num")
head(data0)
names(data0)
```


```{r}
summary(data0$sensitivity_reward)

data0$learn[data0$sensitivity_reward < 0.444]<- "didn't learn"
data0$learn[data0$sensitivity_reward >= 0.444 & data0$sensitivity_reward < 0.5  ]<- "meh"
data0$learn[ data0$sensitivity_reward >= 0.5 & data0$sensitivity_reward < 0.57 ]<- "ok"
data0$learn[ data0$sensitivity_reward >= 0.57]<- "pretty pretty good"
summary(as.factor(data0$learn))

hmTOTALgood<-ggplot(subset(data0, learn == "pretty pretty good"),aes(as.numeric(Count), as.factor(sub_num) ,fill=outcome0))+
  geom_tile()+
  scale_fill_gradient2(low="blue", high="red", na.value="black", name="")+
  geom_point(aes(shape=as.factor(choice), size=1, color=as.factor(choice)))
hmTOTALgood


hmTOTALbad<-ggplot(subset(data0, learn == "didn't learn"),aes(as.numeric(Count), as.factor(sub_num) ,fill=outcome0))+
  geom_tile()+
  scale_fill_gradient2(low="blue", high="red", na.value="black", name="")+
  geom_point(aes(shape=as.factor(choice), size=1, color=as.factor(choice)))
hmTOTALbad

test<-ggarrange(hmTOTALbad,hmTOTALgood, 
          labels = c("bad", "good"),
          ncol = 1, nrow = 2)
```

```{r}

data0$choice0[data0$choice == "Miss"] <- 0
# good
data0$choice0[data0$choice == "A"] <- 30
data0$choice0[data0$choice == "C"] <- 20
data0$choice0[data0$choice == "E"] <- 10
# bad
data0$choice0[data0$choice == "B"] <- -30
data0$choice0[data0$choice == "D"] <- -20
data0$choice0[data0$choice == "F"] <- -10

hmTOTALgood_flip<-ggplot(subset(data0, learn == "pretty pretty good"),aes(as.numeric(Count), as.factor(sub_num) ,fill=choice0))+
  geom_tile()+
  scale_fill_gradient2(low="blue", high="red", na.value="black", name="")
  #geom_point(aes(shape=as.factor(outcome), size=1, color=as.factor(outcome)))
hmTOTALgood_flip


hmTOTALbad_flip<-ggplot(subset(data0, learn == "didn't learn"),aes(as.numeric(Count), as.factor(sub_num) ,fill=choice0))+
  geom_tile()+
  scale_fill_gradient2(low="blue", high="red", na.value="black", name="")
  #geom_point(aes(shape=as.factor(outcome), size=1, color=as.factor(outcome)))
hmTOTALbad_flip

test<-ggarrange(hmTOTALbad_flip,hmTOTALgood_flip, 
          labels = c("bad", "good"),
          ncol = 1, nrow = 2)
```

```{r}
mytable <- xtabs(~choice+learn, data=data0)
ftable(mytable) # print table 
summary(mytable) # chi-square test of indepedence

mytable <- xtabs(~outcome+learn, data=data0)
ftable(mytable) # print table 
summary(mytable) # chi-square test of indepedence


mytable <- xtabs(~congruent+learn, data=data0)
ftable(mytable) # print table 
summary(mytable) # chi-square test of indepedence

```
## Ah ha moment
There is a difference between the number of mismatched trials in the "learners" and "non learners." Those who "don't learn" have more mismatches.
